### 2022-05-26 chapters/execution_environement/python/python.tex
add : tommti benchmark just a single draft have to readit later

\subsection{benchmarks}

\subsection{first results}

@@

\subsection{results and foundings}

>>>>

\begin{figure}
    \caption{energy consumption of different impelementations using Bit Operation benchmarks (Joule) }
    \label{table:bitops}
    \begin{tabular}{lrrrrr}
        \toprule
        benchmark    & A          & GG         & LL         & Or         & XOR        \\
        \midrule
        activepython & 676.980672 & 763.208040 & 651.783048 & 743.016425 & 728.828481 \\
        cpython2     & 441.082298 & 435.886950 & 430.846171 & 415.247383 & 419.081447 \\
        cpython3     & 595.209019 & 685.085315 & 563.839300 & 657.972734 & 655.560574 \\
        cython       & 35.077408  & 182.688395 & 274.177830 & 34.868014  & 34.504778  \\
        nuitka       & 33.260991  & 32.980380  & 33.256450  & 33.472770  & 33.030889  \\
        numba2       & 9.102939   & 8.411176   & 9.460620   & 9.375920   & 9.755952   \\
        numba3       & 9.566646   & 10.144212  & 9.219703   & 9.344613   & 9.665108   \\
        pypy2        & 8.456867   & 7.844918   & 8.286278   & 8.138692   & 7.952999   \\
        pypy3        & 7.552731   & 8.093884   & 8.108508   & 8.669448   & 8.623737   \\
        shedskin     & 8.024198   & 8.070870   & 8.399917   & 8.126236   & 8.277546   \\
        \bottomrule
    \end{tabular}

\end{figure}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\linewidth]{imgs/bitopts_mean}
    \caption{Mean consumption of different implementations of bit operations (Joule) }
    \label{fig:bitops}
\end{figure}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\linewidth]{imgs/alltomti_performance}
    \caption{different interpererts optimisation }
    \label{fig:tommi_all}
\end{figure}
\begin{figure}[thb]
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__pypy2_pypy3}
    \caption{green factor of pypy }
    \label{fig:pypy2vspypy3}
\end{figure}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__cpython3_numba3_pypy3}
    \caption{comparaison of pypy vs python vs numba }
    \label{fig:p3}
\end{figure}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__cpython2_pypy2_numba2}
    \caption{comparaison of pypy vs python vs numba }
    \label{fig:p2}
\end{figure}

\begin{figure}[thb]
    \centering
    \includegraphics[width=\linewidth]{imgs/bar_plot_tommtivector}
    \caption{energy consumption of different impetions treating vectors }
    \label{fig:bar_tommti_vector}
\end{figure}

@@

\subsection{results and foundings}
As we can see in figure \ref{fig:tommi_all}, there is no evolution between cpython2 and cpython3
Intelpython and active python both folows the same behaviour. one can conclude that the work that have been on those interpreters is mainly
to improve a specific purpose, Active python claims that their version is focused on secuirty which explains the lack of some performances due to the introduction of more reonforcment
.Morver Intel published their version of python as a dedicated for machine learning. Unfortunately the tommti benchmark is a set that focuses on the general purpose programming
which does not reflect the performance of the machine learning.
Another aspect of a such behaviour might be due to the fact of the processors that were used in the testbed. and it might change in the future if we include the GPU part for the machine learning benchmarks
% reference the work of the intern 
As for nuitka. there were no optimization in the energy consumpotion despite the fact that is it a complier.
However if we dig through the nuitka mechanisms. they basically embed the python code with an interpreter.
Unllike nuitka shedskin exhebit a the best energy consumption pattern when it comes to the arithmetic operartions. One can conclude it is due to the fact of the native type of the variables. unlike the interpreters where they are treated as object in the begining.

for the other interpeters pypy is very promising especially when it comes to data maniupulation as one can see in the figure \ref{fig:bar_tommti_vector}
pypy is by far the best interperer when it comes to treating vectors.
numba2 introduced the JIT but wasn't as promising as numba3.

for the other vm based interpereters. jython and ipy lacked in term of energy optimisation which was kinda expected since they were in their the begining of the stage and the main puprose of such implementation is to link the bytecode generated by jython and ironpython with their respectives virtual machin.

Unlike the the previous interpeters. graal exhebits a certin promises when it comes to complex algorithms - nested loops -
micro python is dedicated to embeded systems so lunching it is powerful cpu machines will be misleading.

Most of the interperters had the same behaviour when it comes to the input outputs. except for jython which was kinda of a anomaly probably due to the lack of the optimizations.
% pypy handles exceptions very well

%% todo 
% add performance 
% add dram \ a glimps 
% add bitops
